---
output:  
  pdf_document:
    fig_caption: true

---
# **Ordinary Least Squares Single Regression Abundance Models**
**Discussion**
OLS regression models using all lifestages from all surveys with a 1- and 2-yr lag to predict all survey's total CPUEs were constructed to find all explanatory relationships.  All significant relationships are displayed in the following tables.  The CRMS Creek Trawl is the most consistently responsive of the surveys when used in regression modeling.  Fifteen significant relationships exist between total CPUEs from the Creek Trawl survey and several 1- and 2-yr.lagged lifestage variables (Table 3).  The CRMS Harbor Trawl had one significant explanatory relationship with subadults from the same survey lagged 1-yr (Table 4).  The Trammel Net survey had one significant explanatory relatioship with mature females from the Harbor Trawl lagged 1-yr (Table 4), which is the highest correlation (r<sup>2</sup>=0.36) of all the single regression models.  
\newline
Although there were several significant regression models constructed using fisheries independent survey life stage abundance CPUEs, no relationships correlate strong enough to be effective models.  Using OLS single regression modeling, the six SCDNR fisheries independent surveys used to monitor blue crab populations in the Charleston Harbor watershed are ineffective are ineffective predictors of their own abundance CPUEs. 
\newline
The next step in this chapter is to put all relevant variables for the Creek Trawl into an exploratory dredge to find combinations of variables to populate multiple regression models.  These models will be constucted using the suggestions of the dredge.
\newline

```{r, echo=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tinytex)
library(ggplot2)
library(dplyr)
library(tidyr)
library(kableExtra)


theme_set(theme_classic(base_size = 12)+
           theme(panel.grid.major = element_blank(), 
                 panel.grid.minor = element_blank(),
                 panel.background = element_rect(colour = "black", size=0.5))+
           theme(text=element_text(size=12,  family="serif", colour = "black"))+
          theme(axis.text = element_text(colour = "black"))+
          theme(axis.ticks = element_line(colour = "black"))
          )
update_geom_defaults("point",   list(colour = "black"))
update_geom_defaults("line",   list(colour = "black"))
theme_update(plot.title = element_text(hjust = 0.5))
```


```{r, include=FALSE}

options(tinytex.verbose = TRUE)

```

```{r, echo=FALSE, warning=FALSE, include=FALSE}
AbunRegressTable = read.csv("SingleAbundanceRegress.csv") %>%
  rename("Degrees of Freedom" = Degrees.of.Freedom,
         "Explanatory Variable" = Explanatory.Variable,
         "Dependent Variable" = Dependent.Variable,
         "p-value" = p.value,
         "F-statistic" = F.statistic) %>%
  dplyr::select(2, 4:8)

AbunRegressTable2 = read.csv("SingleAbundanceRegressOthers.csv") %>%
  rename("Degrees of Freedom" = Degrees.of.Freedom,
         "Explanatory Variable" = Explanatory.Variable,
         "Dependent Variable" = Dependent.Variable,
         "p-value" = p.value,
         "F-statistic" = F.statistic) %>%
  dplyr::select(2:7)

```

**Table 3:** OLS regression of total Creek Trawl CPUE by all lifestages from all surveys.
```{r T38, include=TRUE, echo=FALSE, warning=FALSE, include=TRUE, dpi=600, fig.cap="Table 3: OLS regression of total Creek Trawl CPUE by all lifestages from all surveys."}

Abun_Table =  kable(AbunRegressTable, "latex", booktabs = T, align = "llcccc") %>%
  kable_styling(latex_options = "scale_down" , font_size = 8) %>%
  add_header_above(c(" " = 2, "Summary Statistics" = 4)) %>%
  column_spec(3:6, width = "6em")

Abun_Table

```


**Table 4:** OLS regression of all non-Creek Trawl survey total CPUEs by all lifestages from all surveys.
```{r non-T38, include=TRUE, echo=FALSE, warning=FALSE, dpi=600, fig.cap="Table 4: OLS regression of all non-Creek Trawl survey total CPUEs by all lifestages from all surveys."}

Abun_Table2 =  kable(AbunRegressTable2, "latex", booktabs = T, align = "llcccc") %>%
  kable_styling(latex_options = "scale_down" , font_size = 8) %>%
  add_header_above(c(" " = 2, "Summary Statistics" = 4)) %>%
  pack_rows("Harbor Trawl", 1,1) %>%
  pack_rows("Trammel Net", 2,2) %>%
  column_spec(3:6, width = "5em") 

Abun_Table2

```
