---
title: "Charleston Harbor Sum Landings Regressions (2003 - present)"
output:
  pdf_document: default
  word_document: default
editor_options: 
  chunk_output_type: inline
---
**Discussion**
Charleston Harbor landings are a  annual sum of all landings for four SCDNR designated reporting areas.  Areas include: Ashley River (02),  Cooper River (10), Wando River (53) and Charleston Harbor (11).  The sum of these four reporting areas are considered Charleston Harbor watershed system-wide total landings in bushels per year.

SCECAP Open Water ($\ge$ 100m creek width) subadult ($\le$ 127mm & >60mm carapace width) clue crab have the most predictive relationship with Charleston Harbor landings when lagged by 1 year (p-value=0.03973, r^2=0.2259).   SCECAP occurs annually June and July since 1999.  SCECAP is a coast-wide, random stratified station survey, which has varying replicates every year.  

A small signal from the CRMS harbor trawl adult crab (127mm carapace width) (p-value=0.04857, r^2=0.1011) is also present.  The CRMS Harbor Trawl survey occurs at least monthly at four fixed stations along a salinity gradient from the Anchorage in the Charlesotn Harbor to the I-526 bridge over the Ashley River (approx. 18 river km).      

Harbor Trawl time series = 1980-2018\newline 
Creek Trawl time series = 1980-2018\newline 
Ashley Potting Survey time series = 1988-2018\newline 
SCECAP Open Water and Tidal Creek Trawl time series = 1999-2018\newline 
Trammel Net Surey time series = 2006-2018\newline 


**Notes**
Formating, including plot grid titles, indvid. plot titles and axes, need to be cleaned up.  

```{r setup, include=FALSE, echo=FALSE}
library(ggplot2)
library(lubridate)
library(tidyr)
library(dplyr)
library(Hmisc)
library(nlme)
library(cowplot)
library(gridExtra)
library(ggpmisc)

theme_set(theme_classic(base_size = 12)+
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_rect(colour = "black", size=0.5))+
            theme(text=element_text(size=12,  family="serif", colour = "black"))+
            theme(axis.text = element_text(colour = "black"))+
            theme(axis.ticks = element_line(colour = "black"))
)
update_geom_defaults("point",   list(colour = "black"))
update_geom_defaults("line",   list(colour = "black"))
theme_update(plot.title = element_text(hjust = 0.5))
```


```{r Data Read-In, include=FALSE, warning=FALSE, message=FALSE}
#crabdata <- read.csv("ClassSizeAbunMANUAL.csv", stringsAsFactors = FALSE) 
#crabdata = distinct(crabdata, Coll, .keep_all = TRUE) %>%
  #mutate(StartTime = as.character(StartTime)) %>%
  #mutate(StartTime = mdy(StartTime))
#Source = "R.Project$crab - size - classSize - ClassSizeAbunMANUAL2" - file was manually lubridated in Excel
#Keeping for Prosperity

crabdata <- read.csv("ClassSizeAbunDistinct_201912.csv", stringsAsFactors = FALSE)


#Source - Eric Hiltz OFM Fisheries Statistics
#Wrangled in Excel due to confidentiality
depend <- read.csv("MonthlyDependent.csv")

```

```{r Data Wrangling, include=FALSE, warning=FALSE, message=FALSE}
B90T38 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% c("B90", "T38")) %>%
  rename(Total = CPUE,
         Juvenile = JuvCPUE,
         Subadult = SubadultCPUE,
         Adult = AdultCPUE,
         ImmatureFemale = ImmatureFemaleCPUE,
         MatureFemale = MatureFemaleCPUE,
         ImmatureMale = ImmatureMaleCPUE,
         MatureMale = MatureMaleCPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE) %>%
  gather("Lifestage", "CPUE", 5:14) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

T06 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "T06") %>%
  rename(Total = CPUE) %>%
  select(1:5) %>%
  gather("Lifestage", "CPUE", 5) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 


P88 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "P88") %>%
  rename(Total = CPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE) %>%
  distinct(Coll, .keep_all = TRUE) %>%
  select(1:5, 13, 14) %>%
  gather("Lifestage", "CPUE", 5:7) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

p88Crab = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "P88") 


SCECAP = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% c("E98", "E99")) %>%
  rename(Total = CPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE,
         Juvenile = JuvCPUE,
         Subadult = SubadultCPUE,
         Adult = AdultCPUE) %>%
  select(1:8, 13, 14) %>%
  gather("Lifestage", "CPUE", 5:10) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

crab1 = rbind(B90T38, P88) %>%
  rbind(., T06) %>%
  rbind(., SCECAP)



#Joining Independent and Dependent 
crab3 = full_join(crab1, depend,
                  by = c("ProjID", "StationCode", "Year", 
                         "Month", "Lifestage", "CPUE")) %>%
  mutate(ProjID = as.factor(ProjID)) %>%
  mutate(Coll = as.factor(Coll)) %>%
  mutate(StationCode = as.factor(StationCode)) %>%
  mutate(StartTime = ymd(StartTime)) %>%
  mutate(Year = as.numeric(Year)) %>%
  mutate(Month = as.factor(Month)) %>%
  mutate(Lifestage = as.factor(Lifestage)) %>%
  group_by(ProjID, StationCode, Lifestage, Month) %>%
  mutate(Means = mean(CPUE, na.rm=TRUE),
         SDs = sd(CPUE, na.rm=TRUE),
         Zs = (CPUE-Means)/ifelse(SDs>0,SDs, 0.00000001)) %>%
  ungroup() 

unique(crab3$ProjID)

crab = crab3 %>%
  mutate(ProjID = recode(ProjID, 'B90' = "Harbor Trawl",
                         'T38' = "Creek Trawl",
                         'T06' = "Trammel Net",
                         'P88' = "Ashley Potting",
                         'E98' = "SCECAP Creek Trawl",
                         'E99' = "SCECAP Harbor Trawl"))
#crab$CPUE[is.infinite(crab$CPUE)] <- NA


Landings = crab %>%
  filter(ProjID == c("LandingsSum", "LandingsCPUEMean")) %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  select(1,3,4) %>%
  spread(ProjID, CPUE) %>%
  filter(Year > 1979)


B90Abun = crab %>%
  filter(ProjID %in% "Harbor Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:12)


T38Abun = crab %>%
  filter(ProjID %in% "Creek Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:12) 


P88Abun = crab %>%
  filter(ProjID %in% "Ashley Potting") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:4) 

E98Abun = crab %>%
  filter(ProjID %in% "SCECAP Creek Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:8) 


E99Abun = crab %>%
  filter(ProjID %in% "SCECAP Harbor Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:8) 


T06Abun = crab %>%
  filter(ProjID %in% "Trammel Net") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2, 3) 


B90crabAbun03 = full_join(B90Abun, Landings, by = "Year") %>%
  filter(Year > 2002)
T38crabAbun03 = full_join(T38Abun, Landings, by = "Year") %>%
  filter(Year > 2002)
P88crabAbun03 = full_join(P88Abun, Landings, by = "Year") %>%
  filter(Year > 2002)
E98crabAbun03 = full_join(E98Abun, Landings, by = "Year") %>%
  filter(Year > 2002)
E99crabAbun03 = full_join(E99Abun, Landings, by = "Year") %>%
  filter(Year > 2002)

```


```{r Figure 2 (LandingsSum ~ Harbor Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in bushels by CRMS Harbor Trawl abundance CPUEs (independent variables) for years 2003-2018.  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.", fig.width=10,fig.height=11}

#Landings ~ Total
formulaB90_T03 = lm(B90crabAbun03$LandingsSum ~ B90crabAbun03$Total)
B90TotalLandings03Plot = ggplot(aes(Total, LandingsSum), data = B90crabAbun03) +
  ggtitle("Charleston Harbor Landings 03-18 \nby Harbor Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_T03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaB90_T03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#Landings ~ Adult
formulaB90_A03 = lm(B90crabAbun03$LandingsSum ~ B90crabAbun03$Adult)
B90AdultLandings03Plot = ggplot(aes(Adult, LandingsSum), data = B90crabAbun03) +
  ggtitle("Charleston Harbor Landings 03-18 \nby Harbor Trawl Adult (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_A03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaB90_A03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#Landings ~ lag(Subadult)
formulaB90_SA03 = lm(B90crabAbun03$LandingsSum ~ lag(B90crabAbun03$Subadult))
B90SubadultLandings03Plot = ggplot(aes(lag(Subadult), LandingsSum), data = B90crabAbun03) +
  ggtitle("Charleston Harbor Landings 03-18 \nby lagged (1 yr.) Harbor Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_SA03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaB90_SA03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#Landings ~ lag(Juvenile)
formulaB90_J03 = lm(lead(B90crabAbun03$LandingsSum) ~ lag(B90crabAbun03$Juvenile))
B90JuvenilLandings03Plot = ggplot(aes(lag(Juvenile), LandingsSum), data = B90crabAbun03) +
  ggtitle("Charleston Harbor Landings 03-18 \nby lagged (2 yr.) Harbor Trawl Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_J03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.11,
               formula = formulaB90_J03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

B90SizeLandingsRegress03 <- plot_grid(B90TotalLandings03Plot, B90AdultLandings03Plot, B90SubadultLandings03Plot, B90JuvenilLandings03Plot, 
                                    ncol = 1, align = 'hv')
B90SizeLandingsRegress03
```

```{r Figure 2 (LandingsSum ~ Creek Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in bushels by CRMS Creek Trawl abundance CPUEs (independent variables) for years 2003-2018.  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.", fig.width=10,fig.height=11}
#Landings ~ Total
formulaT38_T03 = lm(T38crabAbun03$LandingsSum ~ T38crabAbun03$Total)
T38TotalLandings03Plot = ggplot(aes(Total, LandingsSum), data = T38crabAbun03) +
  ggtitle("Charleston Harbor Watershed Landings (2003-2018) \nby Creek Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_T03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaT38_T03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(blue~crab~landings~(bu.)~per~year^{-1}),
       x=expression(blue~crab~abundance~per~trawl^{-1}))


#Landings ~ Adult
formulaT38_A03 = lm(T38crabAbun03$LandingsSum ~ T38crabAbun03$Adult)
T38AdultLandings03Plot = ggplot(aes(Adult, LandingsSum), data = T38crabAbun03) +
  ggtitle("Charleston Harbor Landings (2003-2018) \nby Creek Trawl Adult (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_A03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaT38_A03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#Landings ~ lag(Subadult)
formulaT38_SA03 = lm(T38crabAbun03$LandingsSum ~ lag(T38crabAbun03$Subadult))
T38SubadultLandings03Plot = ggplot(aes(lag(Subadult), LandingsSum), data = T38crabAbun03) +
  ggtitle("Charleston Creek Landings (2003-2018) \nby lagged (1 yr.) Creek Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_SA03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaT38_SA03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#Landings ~ lag(Juvenile)
formulaT38_J03 = lm(lead(T38crabAbun03$LandingsSum) ~ lag(T38crabAbun03$Juvenile))
T38JuvenilLandings03Plot = ggplot(aes(lag(Juvenile), LandingsSum), data = T38crabAbun03) +
  ggtitle("Charleston Creek Landings (2003-2018) \nby lagged (2 yr.) Creek Trawl Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_J03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaT38_J03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


T38SizeLandings03Regress <- plot_grid(T38TotalLandings03Plot, T38AdultLandings03Plot, T38SubadultLandings03Plot, T38JuvenilLandings03Plot, 
                                    ncol = 1, align = 'hv')
T38SizeLandings03Regress
```

```{r Figure 3 (Landings ~ Ashley Potting Survey Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in bushels by Ashley River potting survey abundance CPUEs (independent variables).  Mean annual sublegal CPUEs (<127mm carapace width) are lagged 1 year", fig.width=10,fig.height=11}
#Landings ~ Legal
formulaP88_L03 = lm(P88crabAbun03$LandingsSum ~ P88crabAbun03$Legal)
P88LegalLandings03Plot = ggplot(aes(Legal, LandingsSum), data = P88crabAbun03) +
  ggtitle("Charleston Harbor Landings  \nby Ashley Potting Survey Legal-Sized (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaP88_L03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaP88_L03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~soak^{-1}))


#Landings ~ lag(Sublegal)
formulaP88_SL03 = lm(P88crabAbun03$LandingsSum ~ lag(P88crabAbun03$Sublegal))
P88SublegalLandings03Plot = ggplot(aes(lag(Sublegal), LandingsSum), data = P88crabAbun03) +
  ggtitle("Charleston Harbor Landings  \nby Ashley Potting Survey Sublegal-Sized (<127mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaP88_SL03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaP88_SL03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~soak^{-1}))

P88SizeLandingsRegress03 <- plot_grid(P88LegalLandings03Plot, P88SublegalLandings03Plot, 
                                    ncol = 1, align = 'hv')
P88SizeLandingsRegress03

```

```{r Figure 4 (Landings ~ SCECAP Tidal Creek Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in bushels by SCECAP Tidal Creek Trawl (<100m width) CPUEs (independent variables).  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.  Independent variables were logarithmically transformed due to a large outlier", fig.width=10,fig.height=11}
formulaE98_T03 = lm(E98crabAbun03$LandingsSum ~ E98crabAbun03$Total)
E98TotalLandings03Plot = ggplot(aes(log(Total), LandingsSum), data = E98crabAbun03) +
  ggtitle("Charleston Harbor Landings  \nby SCECAP Open Water Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_T03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.15,
               formula = formulaE98_T03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#Landings ~ Adult
formulaE98_A03 = lm(E98crabAbun03$LandingsSum ~ E98crabAbun03$Adult)
E98AdultLandings03Plot = ggplot(aes(log(Adult), LandingsSum), data = E98crabAbun03) +
  ggtitle("Charleston Harbor Landings  \nby SCECAP Creek Trawl Adult (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_A03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.15,
               formula = formulaE98_A03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#Landings ~ lag(Subadult)
formulaE98_SA03 = lm(E98crabAbun03$LandingsSum ~ lag(E98crabAbun03$Subadult))
E98SubadultLandings03Plot = ggplot(aes(lag(log(Subadult)), LandingsSum), data = E98crabAbun03) +
  ggtitle("Charleston Harbor Landings  \nby lagged (1 yr.) Creek Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_SA03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaE98_SA03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#Landings ~ lag(Juvenile)
formulaE98_J03 = lm(lead(E98crabAbun03$LandingsSum) ~ lag(E98crabAbun03$Juvenile))
E98JuvenilLandings03Plot = ggplot(aes(lag(log(Juvenile)), LandingsSum), data = E98crabAbun03) +
  ggtitle("Charleston Creek Landings (2003-2018) \nby lagged (2 yr.) SCECAPCreek Trawl Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_J03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaE98_J03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1})) 

E98SizeLandings03Regress <- plot_grid(E98TotalLandings03Plot, E98AdultLandings03Plot, 
                                    E98SubadultLandings03Plot, E98JuvenilLandings03Plot, 
                                    ncol = 1, align = 'hv')
E98SizeLandings03Regress

```

```{r Figure 5 (Landings ~ SCECAP Open Water Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in bushels by SCECAP Open Water Trawl (>100m width) CPUEs (independent variables).  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.", fig.width=10,fig.height=11}

#Landings ~ Total
formulaE99_T03 = lm(E99crabAbun03$LandingsSum ~ E99crabAbun03$Total)
E99TotalLandings03Plot = ggplot(aes(Total, LandingsSum), data = E99crabAbun03) +
  ggtitle("Charleston Harbor Landings  \nby Harbor Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_T03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaE99_T03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#Landings ~ Adult
formulaE99_A03 = lm(E99crabAbun03$LandingsSum ~ E99crabAbun03$Adult)
E99AdultLandings03Plot = ggplot(aes(Adult, LandingsSum), data = E99crabAbun03) +
  ggtitle("Charleston HarborLandings  \nby SCECAP Open Water Trawl Adult (>126mm) Abundance CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_A03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaE99_A03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#Landings ~ lag(Subadult)
formulaE99_SA03 = lm(E99crabAbun03$LandingsSum ~ lag(E99crabAbun03$Subadult))
E99SubadultLandings03Plot = ggplot(aes(lag(Subadult), LandingsSum), data = E99crabAbun03) +
  ggtitle("Charleston Creek Landings  \nby lagged (1 yr.) Open Water Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_SA03),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.15,
               formula = formulaE99_SA03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1})) 

#Landings ~ lag(Juvenile)
formulaE99_J03 = lm(lead(E99crabAbun03$LandingsSum) ~ lag(E99crabAbun03$Juvenile))
E99JuvenilLandings03Plot = ggplot(aes(lag(Juvenile), LandingsSum), data = E99crabAbun03) +
  ggtitle("Charleston Creek Landings  \nby lagged (2 yr.) SCECAPCreek Open Water Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_J03),
                  label.x = "right",
                  label.y = "centre",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaE99_J03,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

E99SizeLandings03Regress <- plot_grid(E99TotalLandings03Plot, E99AdultLandings03Plot, E99SubadultLandings03Plot,
                                    E99JuvenilLandings03Plot, 
                                    ncol = 1, align = 'hv')
E99SizeLandings03Regress
```

