---
title: "Ch1_TimeSeries"
author: "Stephen Czwartacki"
date: "December 19, 2019"
output: pdf_document
---
---
title: "Chapter 1 Time Series  \nAll Abundance Surveys and Landings"
output:
  pdf_document: default
  word_document: default
editor_options: 
  chunk_output_type: inline
---
**Discussion**
Mean annual blue crab abundances from South Carolina Department of Natural Resources (SCDNR) fisheries independent population surveys and landings from fisheries dependent SCDNR landings data show high annual variability.

```{r setup, include=FALSE, echo=FALSE}
library(ggplot2)
library(lubridate)
library(tidyr)
library(dplyr)
library(Hmisc)
library(nlme)
library(cowplot)
library(gridExtra)
library(ggpmisc)

theme_set(theme_classic(base_size = 12)+
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_rect(colour = "black", size=0.5))+
            theme(text=element_text(size=12,  family="serif", colour = "black"))+
            theme(axis.text = element_text(colour = "black"))+
            theme(axis.ticks = element_line(colour = "black"))
)
update_geom_defaults("point",   list(colour = "black"))
update_geom_defaults("line",   list(colour = "black"))
theme_update(plot.title = element_text(hjust = 0.5))
```

```{r Data Read-In, include=FALSE, warning=FALSE, message=FALSE}

crabdata <- read.csv("ClassSizeAbunDistinct_201912.csv", stringsAsFactors = FALSE)

```

```{r Data Wrangling, include=FALSE, warning=FALSE, message=FALSE}
B90T38 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% c("B90", "T38")) %>%
  rename(Total = CPUE,
         Juvenile = JuvCPUE,
         Subadult = SubadultCPUE,
         Adult = AdultCPUE,
         "Immature Female" = ImmatureFemaleCPUE,
         "Mature Female" = MatureFemaleCPUE,
         "Immature Male" = ImmatureMaleCPUE,
         "Mature Male" = MatureMaleCPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE) %>%
  gather("Lifestage", "CPUE", 5:14) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

T06 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "T06") %>%
  rename(Total = CPUE) %>%
  select(1:5) %>%
  gather("Lifestage", "CPUE", 5) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 


P88 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "P88") %>%
  rename(Total = CPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE) %>%
  distinct(Coll, .keep_all = TRUE) %>%
  select(1:5, 13, 14) %>%
  gather("Lifestage", "CPUE", 5:7) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

p88Crab = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "P88") 


SCECAP = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% c("E98", "E99")) %>%
  rename(Total = CPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE,
         Juvenile = JuvCPUE,
         Subadult = SubadultCPUE,
         Adult = AdultCPUE) %>%
  select(1:8, 13, 14) %>%
  gather("Lifestage", "CPUE", 5:10) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

crab1 = rbind(B90T38, P88) %>%
  rbind(., T06) %>%
  rbind(., SCECAP)



#Source - Eric Hiltz OFM Fisheries Statistics
#Wrangled in Excel due to confidentiality
depend <- read.csv("MonthlyDependent.csv")


#Joining Independent and Dependent 
crab3 = full_join(crab1, depend,
                  by = c("ProjID", "StationCode", "Year", 
                         "Month", "Lifestage", "CPUE")) %>%
  mutate(ProjID = as.factor(ProjID)) %>%
  mutate(Coll = as.factor(Coll)) %>%
  mutate(StationCode = as.factor(StationCode)) %>%
  mutate(StartTime = ymd(StartTime)) %>%
  mutate(Year = as.numeric(Year)) %>%
  mutate(Month = as.factor(Month)) %>%
  mutate(Lifestage = as.factor(Lifestage)) %>%
  group_by(ProjID, StationCode, Lifestage, Month) %>%
  mutate(Means = mean(CPUE, na.rm=TRUE),
         SDs = sd(CPUE, na.rm=TRUE),
         Zs = (CPUE-Means)/ifelse(SDs>0,SDs, 0.00000001)) %>%
  ungroup() 

#### IS.FINITE NEEDS TO GO HERE FOR mATURE fEMALE STAT_SUMMS AND GEOM_HLINES

crab = crab3 %>%
  mutate(ProjID = recode(ProjID, 'B90' = "Harbor Trawl",
                         'T38' = "Creek Trawl",
                         'T06' = "Trammel Net",
                         'P88' = "Ashley Potting",
                         'E98' = "SCECAP Creek Trawl",
                         'E99' = "SCECAP Harbor Trawl"))


```


```{r Figure 1 (Landings and LandingsCPUE Time Series), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Total Annual blue crab Landings and mean annual landings CPUE (mean ± standard error) for all reporting areas within the Charleston Harbor watershed (including Ashley, Wando and Cooper Rivers and Charleston Harbor).", fig.width=10,fig.height=11}
LandingsCPUEFormTotal = subset(crab,
                           ProjID == "LandingsCPUEMean")

formula1 <- lm(LandingsCPUEFormTotal$CPUE ~ LandingsCPUEFormTotal$Year)

LandingsCrab = crab %>%
  filter(ProjID == c("LandingsSum", "LandingsCPUEMean")) %>%
  group_by(ProjID) %>%
  mutate(Means = mean(CPUE, na.rm=TRUE),
         SDs = sd(CPUE, na.rm=TRUE),
         Zs = (CPUE-Means)/ifelse(SDs>0,SDs, 0.00000001)) %>%
  ungroup() 


LandingsCPUE = ggplot(aes(Year, CPUE), data = subset(LandingsCrab,
                                                     ProjID == "LandingsCPUEMean")) +
  ggtitle("Mean Annual Landings CPUE\nCharleston Harbor (Combined Watersheds)") +
  geom_hline(aes(yintercept=mean(CPUE)), linetype="dashed") +
  stat_summary(fun.data = "mean_se", size = .7) +
  stat_poly_eq(aes(label = ..eq.label..), formula = formula1, parse = TRUE) +
  geom_smooth(method = 'loess', se=FALSE, color="black") +
  labs(y=expression(Blue~crab~~per~pot~fished^{-1})) +
  expand_limits(x=c(1980, 2022))




LandingsFormTotal = subset(crab,
                      ProjID == "LandingsSum")
formula2 <- lm(LandingsFormTotal$CPUE ~ LandingsFormTotal$Year)
Landings = ggplot(aes(Year, CPUE), data = subset(LandingsCrab,
                                                 ProjID == "LandingsSum")) +
  ggtitle("Total Annual Landings\nCharleston Harbor (Combined Watersheds)") +
  geom_hline(aes(yintercept=mean(CPUE)), linetype="dashed") +
  stat_summary(fun.data = "mean_se", size = .7) +
  stat_poly_eq(aes(label = ..eq.label..), formula = formula2, parse = TRUE) +
  geom_smooth(method = 'loess', se=FALSE, color="black") +
  labs(y=expression(Blue~crab~lbs.~per~year^{-1})) +
  expand_limits(x=c(1980, 2022))



LandingsFormTotal04 = subset(crab,
                      ProjID == "LandingsSum" &
                        Year > 2002)
formula3 <- lm(LandingsFormTotal04$CPUE ~ LandingsFormTotal04$Year)
Landings04 = ggplot(aes(Year, CPUE), data = subset(LandingsCrab,
                                                 ProjID == "LandingsSum" &
                                                   Year > 2002)) +
  ggtitle("Total Annual Landings\nCharleston Harbor (Combined Watersheds)") +
  geom_hline(aes(yintercept=mean(CPUE)), linetype="dashed") +
  stat_summary(fun.data = "mean_se", size = .7) +
  stat_poly_eq(aes(label = ..eq.label..), formula = formula3, parse = TRUE) +
  geom_smooth(method = 'loess', se=FALSE, color="black") +
  labs(y=expression(Blue~crab~lbs.~per~year^{-1})) +
  expand_limits(x=c(1980, 2022))


LandingsTimeSeries <- plot_grid(Landings, Landings04, LandingsCPUE, ncol = 1, align = 'hv')
LandingsTimeSeries



```

Landings are a sum of total pounds of landings accross all reporting areas in the Charleston Harbor watershed from 1972-2018. These data show crab landings reported in the Ashley River (2003-2018), Cooper River (2003-2018), Wando River (1974, 1978-2018) and Charleston Harbor (1972-2018).  Landings from 2003 to 2018 are the only time period covering all 4 reporting areas.  Standard error bars for these total sum landings show a sum total monthly range across all reporting areas.  

Landings CPUE are landings with number of pots pulled as a metric of fishing effort.  These mean annual data were computed as a sum total of lbs by month/year









