---
title: "Index of Abundance Using  \nSum Landings for Charleston Harbor  \n(Total Lbs. Landed/# Pots Pulled)"
output:
  pdf_document: default
  word_document: default
editor_options: 
  chunk_output_type: inline
---

**Discussion**
MRK - I need help.
I don't know what's going on with these results, as they show no significant relationship between Landings CPUE and any of the abundance metrics! These relationships were the best I'd ofund in previous data exploration.  I did have to recalculate the way I counted mature female, but that should have nothing to do with the size (Juv, Subadult and adult) regressions.  I trust my code from the exploratory analyses from earlier better than this, but this is good plot code.  I should be able to fix the input data when I sniff out what is going on.  It could be the way I built the lm for the poly_stat_eq...

```{r setup, include=FALSE, echo=FALSE}
library(ggplot2)
library(lubridate)
library(tidyr)
library(dplyr)
library(Hmisc)
library(nlme)
library(cowplot)
library(gridExtra)
library(ggpmisc)

theme_set(theme_classic(base_size = 12)+
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_rect(colour = "black", size=0.5))+
            theme(text=element_text(size=12,  family="serif", colour = "black"))+
            theme(axis.text = element_text(colour = "black"))+
            theme(axis.ticks = element_line(colour = "black"))
)
update_geom_defaults("point",   list(colour = "black"))
update_geom_defaults("line",   list(colour = "black"))
theme_update(plot.title = element_text(hjust = 0.5))
```

```{r Data Read-In, include=FALSE, warning=FALSE, message=FALSE}
crabdata <- read.csv("ClassSizeAbunMANUAL.csv", stringsAsFactors = FALSE) 
crabdata = distinct(crabdata, Coll, .keep_all = TRUE) %>%
  mutate(StartTime = as.character(StartTime)) %>%
  mutate(StartTime = mdy(StartTime))
#Source = "R.Project$crab - size - classSize - ClassSizeAbunMANUAL2" - file was manually lubridated in Excel
#This data is cleandata from the crab project with abundance information for both size and class of crab


#Source - Eric Hiltz OFM Fisheries Statistics
#Wrangled in Excel due to confidentiality
depend <- read.csv("hardCrabsByArea_04252019_CH.csv")

```

```{r Data Wrangling, include=FALSE, warning=FALSE, message=FALSE}
B90T38 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% c("B90", "T38")) %>%
  rename(Total = CPUE,
         Juvenile = JuvCPUE,
         Subadult = SubadultCPUE,
         Adult = AdultCPUE,
         ImmatureFemale = ImmatureFemaleCPUE,
         MatureFemale = MatureFemaleCPUE,
         ImmatureMale = ImmatureMaleCPUE,
         MatureMale = MatureMaleCPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE) %>%
  gather("Lifestage", "CPUE", 5:14) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

T06 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "T06") %>%
  rename(Total = CPUE) %>%
  select(1:5) %>%
  gather("Lifestage", "CPUE", 5) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 


P88 = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "P88") %>%
  rename(Total = CPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE) %>%
  distinct(Coll, .keep_all = TRUE) %>%
  select(1:5, 13, 14) %>%
  gather("Lifestage", "CPUE", 5:7) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

p88Crab = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% "P88") 


SCECAP = crabdata %>% #Formerly crab1
  select(1:4, 7:16) %>%
  filter(ProjID %in% c("E98", "E99")) %>%
  rename(Total = CPUE,
         Sublegal = SublegalCPUE,
         Legal = LegalCPUE,
         Juvenile = JuvCPUE,
         Subadult = SubadultCPUE,
         Adult = AdultCPUE) %>%
  select(1:8, 13, 14) %>%
  gather("Lifestage", "CPUE", 5:10) %>%
  mutate(Year = year(StartTime)) %>%
  mutate(Month = month(StartTime)) %>%
  select(1,2,4,3,7,8,5,6) 

crab1 = rbind(B90T38, P88) %>%
  rbind(., T06) %>%
  rbind(., SCECAP)



#Joining Independent and Dependent 
crab3 = full_join(crab1, depend,
                  by = c("ProjID", "StationCode", "Year", 
                         "Month", "Lifestage", "CPUE")) %>%
  mutate(ProjID = as.factor(ProjID)) %>%
  mutate(Coll = as.factor(Coll)) %>%
  mutate(StationCode = as.factor(StationCode)) %>%
  mutate(StartTime = ymd(StartTime)) %>%
  mutate(Year = as.numeric(Year)) %>%
  mutate(Month = as.factor(Month)) %>%
  mutate(Lifestage = as.factor(Lifestage)) %>%
  group_by(ProjID, StationCode, Lifestage, Month) %>%
  mutate(Means = mean(CPUE, na.rm=TRUE),
         SDs = sd(CPUE, na.rm=TRUE),
         Zs = (CPUE-Means)/ifelse(SDs>0,SDs, 0.00000001)) %>%
  ungroup() 

#### IS.FINITE NEEDS TO GO HERE FOR mATURE fEMALE STAT_SUMMS AND GEOM_HLINES

crab = crab3 %>%
  mutate(ProjID = recode(ProjID, 'B90' = "Harbor Trawl",
                         'T38' = "Creek Trawl",
                         'T06' = "Trammel Net",
                         'P88' = "Ashley Potting",
                         'E98' = "SCECAP Creek Trawl",
                         'E99' = "SCECAP Harbor Trawl"))
crab$CPUE[is.infinite(crab$CPUE)] <- NA


Landings = crab %>%
  filter(ProjID == c("Landings", "LandingsCPUE")) %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  select(1,3,4) %>%
  spread(ProjID, CPUE) %>%
  filter(Year > 1979)


B90Abun = crab %>%
  filter(ProjID %in% "Harbor Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:12)


T38Abun = crab %>%
  filter(ProjID %in% "Creek Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:12) 


P88Abun = crab %>%
  filter(ProjID %in% "Ashley Potting") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:4) 

E98Abun = crab %>%
  filter(ProjID %in% "SCECAP Creek Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:8) 


E99Abun = crab %>%
  filter(ProjID %in% "SCECAP Harbor Trawl") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2:8) 


T06Abun = crab %>%
  filter(ProjID %in% "Trammel Net") %>%
  group_by(ProjID, Lifestage, Month, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(ProjID, Lifestage, Year) %>%
  summarise_at(vars(CPUE), funs(mean(., na.rm = TRUE))) %>%
  ungroup() %>%
  spread(Lifestage, CPUE) %>%
  select(2, 3) 


B90crabAbun = full_join(B90Abun, Landings, by = "Year")
T38crabAbun = full_join(T38Abun, Landings, by = "Year")
P88crabAbun = full_join(P88Abun, Landings, by = "Year")
E98crabAbun = full_join(E98Abun, Landings, by = "Year")
E99crabAbun = full_join(E99Abun, Landings, by = "Year")

```

```{r Figure 1 (LandingsCPUE ~ Harbor Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in total poundslanded/# pots pulled by CRMS Harbor Trawl abundance CPUEs (independent variables).  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.", fig.width=10,fig.height=11}


#LandingsCPUE ~ Total
formulaB90_T = lm(B90crabAbun$LandingsCPUE ~ B90crabAbun$Total)
B90TotalLandingsCPUEPlot = ggplot(aes(Total, LandingsCPUE), data = B90crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby Harbor Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_T),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaB90_T,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#LandingsCPUE ~ Adult
formulaB90_A = lm(B90crabAbun$LandingsCPUE ~ B90crabAbun$Adult)
B90AdultLandingsCPUEPlot = ggplot(aes(Adult, LandingsCPUE), data = B90crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby Harbor Trawl Adult (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_A),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaB90_A,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#LandingsCPUE ~ lag(Subadult)
formulaB90_SA = lm(B90crabAbun$LandingsCPUE ~ lag(B90crabAbun$Subadult))
B90SubadultLandingsCPUEPlot = ggplot(aes(lag(Subadult), LandingsCPUE), data = B90crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby lagged (1 yr.) Harbor Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_SA),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
  #label.x.npc = "right", label.y.npc = 0.11,
  #formula = formulaB90_SA,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#LandingsCPUE ~ lag(Juvenile)
formulaB90_J = lm(lead(B90crabAbun$LandingsCPUE) ~ lag(B90crabAbun$Juvenile))
B90JuvenilLandingsCPUEPlot = ggplot(aes(lag(Juvenile), LandingsCPUE), data = B90crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby Lagged (2 yr.) Harbor Trawl Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaB90_J),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
  #label.x.npc = "right", label.y.npc = 0.11,
  #formula = formulaB90_J,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

B90SizeLandingsCPUERegress <- plot_grid(B90TotalLandingsCPUEPlot, B90AdultLandingsCPUEPlot,
                                        B90SubadultLandingsCPUEPlot, B90JuvenilLandingsCPUEPlot, 
                                        ncol = 1, align = 'hv')
B90SizeLandingsCPUERegress
```

```{r Figure 2 (LandingsCPUE ~ Creek Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in total pounds landed/# pots pulled by CRMS Creek Trawl abundance CPUEs (independent variables).  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.", fig.width=10,fig.height=11}
formulaT38_T = lm(T38crabAbun$LandingsCPUE ~ T38crabAbun$Total)
T38TotalLandingsCPUEPlot = ggplot(aes(Total, LandingsCPUE), data = T38crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby Creek Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_T),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaT38_T,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#LandingsCPUE ~ Adult
formulaT38_A = lm(T38crabAbun$LandingsCPUE ~ T38crabAbun$Adult)
T38AdultLandingsCPUEPlot = ggplot(aes(Adult, LandingsCPUE), data = T38crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby Creek Trawl Adult (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_A),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaT38_A,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#LandingsCPUE ~ lag(Subadult)
formulaT38_SA = lm(T38crabAbun$LandingsCPUE ~ lag(T38crabAbun$Subadult))
T38SubadultLandingsCPUEPlot = ggplot(aes(lag(Subadult), LandingsCPUE), data = T38crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby lagged (1 yr.) Creek Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_SA),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaT38_SA,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#LandingsCPUE ~ lag(Juvenile)
formulaT38_J = lm(lead(T38crabAbun$LandingsCPUE) ~ lag(T38crabAbun$Juvenile))
T38JuvenilLandingsCPUEPlot = ggplot(aes(lag(Juvenile), LandingsCPUE), data = T38crabAbun) +
  ggtitle("Charleston Creek Landings CPUE  \nby lagged (2 yr.) CRMS Creek Trawl Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaT38_J),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaT38_J,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

T38SizeLandingsCPUERegress <- plot_grid(T38TotalLandingsCPUEPlot, T38AdultLandingsCPUEPlot,
                                        T38SubadultLandingsCPUEPlot, T38JuvenilLandingsCPUEPlot, 
                                        ncol = 1, align = 'hv') 
T38SizeLandingsCPUERegress


```

```{r Figure 3 (LandingsCPUE ~ Ashley Potting Survey Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in total lpounds landed/# pots pulled by Ashley River potting survey abundance CPUEs (independent variables).  Mean annual sublegal CPUEs (<127mm carapace width) are lagged 1 year", fig.width=10,fig.height=11}
#LandingsCPUE ~ Legal
formulaP88_L = lm(P88crabAbun$LandingsCPUE ~ P88crabAbun$Legal)
P88LegalLandingsCPUEPlot = ggplot(aes(Legal, LandingsCPUE), data = P88crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby Ashley Potting Survey Legal-Sized (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaP88_L),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaP88_L,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~soak^{-1}))


#LandingsCPUE ~ lag(Sublegal)
formulaP88_SL = lm(P88crabAbun$LandingsCPUE ~ lag(P88crabAbun$Sublegal))
P88SublegalLandingsCPUEPlot = ggplot(aes(lag(Sublegal), LandingsCPUE), data = P88crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby Ashley Potting Survey Sublegal-Sized (<127mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaP88_SL),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaP88_SL,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~soak^{-1}))

P88SizeLandingsCPUERegress <- plot_grid(P88LegalLandingsCPUEPlot, P88SublegalLandingsCPUEPlot, 
                                    ncol = 1, align = 'hv')
P88SizeLandingsCPUERegress


```


```{r Figure 4 (LandingsCPUE ~ SCECAP Tidal Creek Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in total pounds landed/# pots pulled by SCECAP Tidal Creek Trawl (<100m width) CPUEs (independent variables).  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.  Independent variables were logarithmically transformed due to a large outlier", fig.width=10,fig.height=11}
#LandingsCPUE ~ Total
formulaE98_T = lm(E98crabAbun$LandingsCPUE ~ E98crabAbun$Total)
E98TotalLandingsCPUEPlot = ggplot(aes(log(Total), LandingsCPUE), data = E98crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby SCECAP Open Water Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_T),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaE98_T,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#LandingsCPUE ~ Adult
formulaE98_A = lm(E98crabAbun$LandingsCPUE ~ E98crabAbun$Adult)
E98AdultLandingsCPUEPlot = ggplot(aes(log(Adult), LandingsCPUE), data = E98crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE  \nby SCECAP Creek Trawl Adult (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_A),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaE98_A,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#LandingsCPUE ~ lag(Subadult)
formulaE98_SA = lm(E98crabAbun$LandingsCPUE ~ lag(E98crabAbun$Subadult))
E98SubadultLandingsCPUEPlot = ggplot(aes(lag(log(Subadult)), LandingsCPUE), data = E98crabAbun) +
  ggtitle("Charleston Creek Landings CPUE  \nby lagged (1 yr.) Creek Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_SA),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaE98_SA,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#LandingsCPUE ~ lag(Juvenile)
formulaE98_J = lm(lead(E98crabAbun$LandingsCPUE) ~ lag(E98crabAbun$Juvenile))
E98JuvenilLandingsCPUEPlot = ggplot(aes(lag(log(Juvenile)), LandingsCPUE), data = E98crabAbun) +
  ggtitle("Charleston Creek Landings CPUE  \nby lagged (2 yr.) SCECAPCreek Trawl Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE98_J),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaE98_J,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

E98SizeLandingsCPUERegress <- plot_grid(E98TotalLandingsCPUEPlot, E98AdultLandingsCPUEPlot, E98SubadultLandingsCPUEPlot, E98JuvenilLandingsCPUEPlot, 
                                    ncol = 1, align = 'hv')
E98SizeLandingsCPUERegress
```

```{r Figure 5 (LandingsCPUE ~ SCECAP Open Water Trawl Regressions), echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares (OLS) regression of Charleston Harbor watershed (Ashley River, Cooper River, Wando River and Charleston Harbor) total landings (dependent variable) in total pounds landed/# pots pulled by SCECAP Open Water Trawl (>100m width) CPUEs (independent variables).  Mean annual subadult CPUEs (>59mm & <127mm carapace width) are lagged 1 year, and mean annual juvenile CPUEs are lagged 2 years.", fig.width=10,fig.height=11}
#LandingsCPUE ~ Total
formulaE99_T = lm(E99crabAbun$LandingsCPUE ~ E99crabAbun$Total)
E99TotalLandingsCPUEPlot = ggplot(aes(Total, LandingsCPUE), data = E99crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE\nby Harbor Trawl CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_T),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaE99_T,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#LandingsCPUE ~ Adult
formulaE99_A = lm(E99crabAbun$LandingsCPUE ~ E99crabAbun$Adult)
E99AdultLandingsCPUEPlot = ggplot(aes(Adult, LandingsCPUE), data = E99crabAbun) +
  ggtitle("Charleston Harbor Landings CPUE \nby SCECAP Open Water Trawl Adult (>126mm) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_A),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.15,
               #formula = formulaE99_A,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))


#LandingsCPUE ~ lag(Subadult)
formulaE99_SA = lm(E99crabAbun$LandingsCPUE ~ lag(E99crabAbun$Subadult))
E99SubadultLandingsCPUEPlot = ggplot(aes(lag(Subadult), LandingsCPUE), data = E99crabAbun) +
  ggtitle("Charleston CreekLandings CPUE  \nby lagged (1 yr.) Open Water Trawl Subadult (>60mm & <127mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_SA),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaE99_SA,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

#LandingsCPUE ~ lag(Juvenile)
formulaE99_J = lm(lead(E99crabAbun$LandingsCPUE) ~ lag(E99crabAbun$Juvenile))
E99JuvenilLandingsCPUEPlot = ggplot(aes(lag(Juvenile), LandingsCPUE), data = E99crabAbun) +
  ggtitle("Charleston Creek Landings CPUE  \nby lagged (2 yr.) SCECAPCreek Open Water Juvenile (<61mm Carapace Width) CPUE") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = formulaE99_J),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  #stat_poly_eq(aes(label = paste(..rr.label..)), 
               #label.x.npc = "right", label.y.npc = 0.11,
               #formula = formulaE99_J,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Blue~crab~trawl^{-1}))

E99SizeLandingsCPUERegress <- plot_grid(E99AdultLandingsCPUEPlot, E99SubadultLandingsCPUEPlot, E99JuvenilLandingsCPUEPlot, 
                                    ncol = 1, align = 'hv')
E99SizeLandingsCPUERegress

```