---
output: pdf_document
---
**Discussion**
OLS single regression models were constructed using mean annual total CPUEs for all surveys as the dependent varaibale and mean annual CPUEs of every lifestage of every survey with 1- and 2- yr. lags as the explanatory variable - i.e., the mean annual CPUEs of all available blue crab lifestages of all 6 SCDNR fisheries independent surveys were used as independent explanatory variables to predict Harbor Trawl total CPUE.  Results show only the Creek Trawl has consist significant results accross all lifestages lagged (Table 3).  One significant relationship predicting Harbor Trawl CPUEs was found (Table 4), and one significant relationship predicting the Trammel Net survey (Table 4) were found.  Scatterplots for select models showing the highest correlation scores for each survey's total CPUE dependent variable were generated showing none of the models have a high correlation (Figure 16).

Each explanatory variable populating a significant relatioship model will be used to populate an exploratory dredge to suggest multiple regression models.

```{r knitr setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE, echo=FALSE}
library(ggplot2)
library(lubridate)
library(tidyr)
library(dplyr)
library(Hmisc)
library(nlme)
library(cowplot)
library(gridExtra)
library(ggpmisc)

theme_set(theme_classic(base_size = 12)+
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  panel.background = element_rect(colour = "black", size=0.5))+
            theme(text=element_text(size=12,  family="serif", colour = "black"))+
            theme(axis.text = element_text(colour = "black"))+
            theme(axis.ticks = element_line(colour = "black"))
)
update_geom_defaults("point",   list(colour = "black"))
update_geom_defaults("line",   list(colour = "black"))
theme_update(plot.title = element_text(hjust = 0.5))
```

```{r Data Read-In, include=FALSE, warning=FALSE, message=FALSE}

crab <- read.csv("CH1data.csv", stringsAsFactors = FALSE)
crab03 = crab %>%
  filter(Year > 2002)

```

```{r List of B90 Models, include=FALSE, warning=FALSE, message=FALSE}
# B90

#Landings
# NO-yr lag
B90Land_lm4 <- lm(crab$LandingsSum ~ crab$B90_AdultCPUE)
summary(B90Land_lm4) # 0.03084 - 0.1199
B90Land_lm7 <- lm(crab$LandingsSum ~ crab$B90_MatureFemaleCPUE)
summary(B90Land_lm7) # 0.02982 - 0.1213
B90Land_lm8 <- lm(crab$LandingsSum ~ crab$B90_MatureMaleCPUE)
summary(B90Land_lm8) # 0.02406 - 0.1301
B90Land_lm10 <- lm(crab$LandingsSum ~ crab$B90_LegalCPUE)
summary(B90Land_lm10) # 0.03084 - 0.1199

# 1-yr lag
B90LandLAG_lm8 <- lm(crab$LandingsSum ~ lag(crab$B90_MatureMaleCPUE))
summary(B90LandLAG_lm8) #0.04897 - 0.1034


#LandingsCPUEMean
# NO-yr lag
B90CPUE_lm2 <- lm(crab$LandingsCPUEMean ~ crab$B90_JuvCPUE)
summary(B90CPUE_lm2) #0.05115 - 0.2619
B90CPUE_lm5 <- lm(crab$LandingsCPUEMean ~ crab$B90_ImmatureFemaleCPUE)
summary(B90CPUE_lm5) #0.03525 - 0.2981
B90CPUE_lm6 <- lm(crab$LandingsCPUEMean ~ crab$B90_ImmatureMaleCPUE)
summary(B90CPUE_lm6) # 0.03943 - 0.2873

# 1-yr lag
B90CPUELAG_lm1 <- lm(crab$LandingsCPUEMean ~ lag(crab$B90_CPUE))
summary(B90CPUELAG_lm1) # 0.02771 - 0.3208
B90CPUELAG_lm3 <- lm(crab$LandingsCPUEMean ~ lag(crab$B90_SubadultCPUE))
summary(B90CPUELAG_lm3) # 0.01668 - 0.367
B90CPUELAG_lm8 <- lm(crab$LandingsCPUEMean ~ lag(crab$B90_MatureMaleCPUE))
summary(B90CPUELAG_lm8) # 0.007659 - 0.433

```

```{r List of T38 Models, include=FALSE, warning=FALSE, message=FALSE}

# T38
# Landings - NONE

# LandingsCPUEMean
# 1-yr lag
T38CPUELAG_lm1 <- lm(crab$LandingsCPUEMean ~ lag(crab$T38_CPUE))
summary(T38CPUELAG_lm1) # 0.02388 - 0.3346
T38CPUELAG_lm2 <- lm(crab$LandingsCPUEMean ~ lag(crab$T38_JuvCPUE))
summary(T38CPUELAG_lm2) # 0.03014 - 0.3129
T38CPUELAG_lm3 <- lm(crab$LandingsCPUEMean ~ lag(crab$T38_SubadultCPUE))
summary(T38CPUELAG_lm3) # 0.01947 - 0.3532
T38CPUELAG_lm5 <- lm(crab$LandingsCPUEMean ~ lag(crab$T38_ImmatureFemaleCPUE))
summary(T38CPUELAG_lm5) # 0.03321 - 0.3038
T38CPUELAG_lm7 <- lm(crab$LandingsCPUEMean ~ lag(crab$T38_ImmatureMaleCPUE))
summary(T38CPUELAG_lm7) # 0.01042 - 0.4076
T38CPUELAG_lm10 <- lm(crab$LandingsCPUEMean ~ lag(crab$T38_SublegalCPUE))
summary(T38CPUELAG_lm10) # 0.01485 - 0.3772

```

```{r List of P88 Models, include=FALSE, warning=FALSE, message=FALSE}
# 2-yr lag
P88LandLAGLead_lm3 <- lm(lead(crab$LandingsSum) ~ lag(crab$P88_LegalCPUE))
summary(P88LandLAGLead_lm3) # 0.0405 - 0.1464

```

```{r List of T06 Models, include=FALSE, warning=FALSE, message=FALSE}
# NO-yr lag
T06CPUE_lm1 <- lm(crab$LandingsCPUEMean ~ crab$T06_CPUE)
summary(T06CPUE_lm1) # 0.01691 - 0.4182

```

```{r Plot Creation, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
B90CPUELAG_lm8 <- lm(crab$LandingsCPUEMean ~ lag(crab$B90_MatureMaleCPUE, 1))
B90CPUELagPlot = ggplot(aes(LandingsCPUEMean, lag(B90_MatureMaleCPUE, 1)), data = crab) +
  ggtitle("Landings CPUE \nby Harbor Trawl Mature Male (1-yr. lag)") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = B90CPUELAG_lm8),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.12,
               formula = B90CPUELAG_lm8,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Harbor~Trawl~mature~male~CPUE~"(1-yr lag)"~year^{-1}))


T38CPUELAG_lm7 <- lm(crab$LandingsCPUEMean ~ lag(crab$T38_ImmatureMaleCPUE, 1))
T38CPUELAGPlot = ggplot(aes(LandingsCPUEMean, lag(T38_ImmatureMaleCPUE, 2)), data = crab) +
  ggtitle("Landings CPUE \nby Creek Trawl Immature Male (1-yr. lag)") +
  geom_point() +
  stat_fit_glance(method = "lm", method.args = list(formula = T38CPUELAG_lm7),
                  label.x = "right",
                  label.y = "bottom",
                  aes(label = paste("italic(P)*\"-value = \"*", 
                                    signif(..p.value.., digits = 4), sep = "")),
                  parse = TRUE) +
  stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.12,
               formula = T38CPUELAG_lm7,rr.digits = 4,  parse = TRUE, size = 4) +
  geom_smooth(method = 'lm', se=FALSE, color="black") +
  labs(y=expression(Landings~CPUE~year^{-1}),
       x=expression(Creek~Trawl~immature~male~CPUE~"(1-yr lag)"~year^{-1}))



```

```{r Figure 4, echo=FALSE, message=FALSE, warning=FALSE,dpi=600, fig.cap="Ordinary Least Squares regression plots of select significant explanatory relatioships using lagged variables to Charleston Harbor watershed Landings CPUEs.  Mean annual landings CPUE by Harbor Trawl mature males with a 1-yr lag (A), and mean annual landings CPUE by Creek Trawl immature males CPUE with a 1-yr. lag (B).", fig.width=10,fig.height=11}

SingleRegressPlot <- plot_grid(B90CPUELagPlot, T38CPUELAGPlot, ncol = 1, align = 'hv', labels = c("A", "B")) 
SingleRegressPlot

```
